\sysfull

### 2017-08-04 paper/compiler.tex
added some specification about normalization

The analysis uses a heuristic to compute a score for each candidate and places
a boundary at the candidate with the highest score. The heuristic tries to
avoid placing boundaries on loops, to minimize the number of live variables
that must be protected across the new boundary, and to maximize the number of
operations along the path.  A boundary candidate's score is computed as:
%
\begin{equation}
\text{score} = \frac{w_{0} N_{\text{IR}} - w_{1} N_{\text{PV}}}{N_{\text{loop}}},\nonumber
\end{equation}
%
where $N_{\text{IR}}$ is the length of the path being traversed up to the
candidate, $N_{\text{PV}}$ is the number of variables live variables at the
candidate, and $N_{\text{loop}}$ is the product of the loop bounds of all loops
(i.e., nested loops) containing the boundary candidate. \sys normalizes $N_{\text{IR}}$ to the
total number of instructions along the path being traversed. The weights, $w_{0},
w_{1}$ are between zero and one, and are hand-tuned parameters that define the
relative importance of $N_{\text{IR}}$, $N_{\text{PV}}$, and $N_{\text{loop}}$.
We will study the effect of weights in Section~\ref{sec:results_compiler}.

>>>>

The analysis uses a heuristic to compute a score for each candidate and places
a boundary at the candidate with the highest score. The heuristic tries to
avoid placing boundaries on loops, to minimize the number of live variables
that must be protected across the new boundary, and to maximize the number of
operations along the path.  A boundary candidate's score is computed as:
%
\begin{equation}
\text{score} = \frac{w_{0} N_{\text{IR}} - w_{1} N_{\text{PV}}}{N_{\text{loop}}},\nonumber
\end{equation}
%
where $N_{\text{IR}}$ is the length of the path being traversed up to the
candidate, $N_{\text{PV}}$ is the number of variables live variables at the
candidate, and $N_{\text{loop}}$ is the product of the loop bounds of all loops
(i.e., nested loops) containing the boundary candidate. \sys normalizes
$N_{\text{IR}}$ and $N_{\text{PV}}$ to the values among boundary candidates.
The weights, $w_{0}, w_{1}$ are between zero and one, and are
hand-tuned parameters that define the relative importance of $N_{\text{IR}}$,
$N_{\text{PV}}$, and $N_{\text{loop}}$.  We empirically determined these weight
values by measuring the runtime for different weight values across
applications.  We found that varying weights varies runtime by only around 5\%
in most cases and in our experimental evaluation, we used $w_{0} = w_{1} =
0.5$.
